Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-06-05 paper/Analisis.tex
Nscatt Histrograms + text in off center model

\begin{figure}
    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
\end{figure}

\begin{figure}
     \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous

    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
\end{figure}

@@

\begin{figure}%QUITARLA Y COMENTARLA
  \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
 \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
\end{figure}

@@

Now we set up a test model when the photons are placed in an inhomogeneous model,

>>>>

%\begin{figure}
 %   \includegraphics[width=0.54\textwidth]{test4.png}
  %  \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}

%\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
%\end{figure}

\begin{figure*}
     \includegraphics[width=0.40\textwidth]{2dHistogram0t5HOM.png}
     \includegraphics[width=0.40\textwidth]{2dHistogram300t5HOM.png}

    \caption{Histogram of $N_{scatt}$ vs $x$ for the homogeneous distribution, left for $V_{max}=0km/s $, right for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
\end{figure*}

\begin{figure*}
     \includegraphics[width=0.40\textwidth]{2dHistogram50t5.png}
     \includegraphics[width=0.40\textwidth]{2dHistogram300t5.png}

    \caption{Histogram of $N_{scatt}$ vs $x$ for the Central distribution, left for $V_{max}=50km/s $, right for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
\end{figure*}

@@

%\begin{figure}%QUITARLA Y COMENTARLA
 % \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
 %\label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the %homogeneous configuration.} 
%\end{figure}

@@

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig.~\ref{figure:distributions} shows
the distributions we set up.

\begin{figure}
  \includegraphics[width=0.40\textwidth]{Distribution.png}
  \caption{Inhomogeneous distributions of 
 photons, Blue area represents the photons in distribution 1 while red area are the selected photons for distribution 2. The arrow points to the observer position\label{figure:distributions}} 
\end{figure}

In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
distribution 1 and 2, the first effect we see is the asymmetry of the
double peak, in the homogeneous and central distribution we see double
peaks with the same height, while in this case one peak is higher than 
the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
peak is higher than the redshifted, and for distribution 2 the redshifted
peak is the highest.

An other important fact here is the asymmetry of the spectra with respect 
to the line center, in particular photons selected in distribution 1 
present a blueshift in their spectra while photons selected in distribution 
2 present a redshift. This effect becomes stronger as velocity increase 
~\ref{figure:inhomogeneous}

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
 \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ , (left) with $\tau=10^5$, (right) with $\tau=10^6$\label{figure:inhomogeneous}} 
\end{figure*}
